Connecting the Popularity Adjusted Block Model to the Generalized Random Dot Product Graph for Community Detection and Parameter Estimation

### 2021-03-09 summary.Rmd
cleaned up proof of theorem 5 a bit more

By (\ref{eq:mu-zero}) and (\ref{eq:mu-conv}),

\begin{equation} \label{eq:thm5-proof}
r(V_n^{(k)}) - \mu(\hat{V}_n^{(k)}) = r(V_n^{(k)})
\end{equation}

for each $k = 1, ..., K$. If enough points are drawn from each community that 
the corresponding uncorrupted embedding points span a $K$-dimensional subspace
(Theorem 2), then $r(V_n^{(k)}) > 0$.

Then by Theorem 6 of \citet{pmlr-v28-wang13}, (\ref{eq:delta-conv}) and
(\ref{eq:thm5-proof}) imply that the SSC detection property holds as 
$n \to \infty$ with probability 1.

>>>>

The basis of this theorem is Theorem 6 from \citet{pmlr-v28-wang13}, which 
states that the SSC detection property holds if the noise is small enough and 
the subspace inradius is greater than the subspace incoherence for each 
community $k$.

Let $V_{n, -i}^{(k)}$ be $V_n^{(k)}$ with the $i$^th^ entry removed. Suppose 
that for each community $k$, there are enough vertices such that for each $i$, 
$V_{n, -i}^{(k)}$ spans its corresponding subspace (Theorem 2). 
Then $r_n^{(k)} = \min\limits_i r(V_{n, -i}^{(k)}) > 0$. 
Thus by (\ref{eq:mu-conv}), for each $k$, $r_n^{(k)} > \mu_n^{(k)}$ where 
$\mu_n^{(k)} = \mu(\hat{V}_n^{(k)})$ and $n$ is large enough such that 
$\min\limits_{k, i} rank(V_{n, -i}^{(k)}) = K$.

Let $r_n = \min_k r_n^{(k)}$. By (\ref{eq:delta-conv}), 
$\delta_n \stackrel{a.s.}{\to} 0$. Then as $n\to \infty$, 
$\delta_n < \min_k \frac{r_n (r_n^{(k)} - \mu_n^{(k)})}{2 + 7 r_n^{(k)}}$ 
with probability 1.

Thus the conditions for the SSC detection property from Theorem 6 from
\citet{pmlr-v28-wang13} are satisfied almost surely as $n \to \infty$.
